Grand Prix motorcycle racing

### 2020-02-24 inst/skating_analysis.Rmd
slight change to small

```{r}
library("hyper2",quietly=TRUE)
data("skating")
skating_table
```

@@

small <-1e-4  # need a sensible start value satisfying the constraints
start <- c(rep(2*small,3),rep(3*small,2),rep(small,17))

>>>>

```{r}
library("hyper2",quietly=TRUE)
set.seed(0)
data("skating")
skating_table
```

@@

small <- 1e-6  # need a sensible start value satisfying the constraints
start <- c(rep(2*small,3),rep(3*small,2),rep(small,17))
